Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-09-15 manuscript/manuscript.tex
Temporaly disabled todonotes
Modified speed comparison: absolute times replaced by computation times ratio

\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{todonotes} % to make annotations on margins
%~ \usepackage[disable]{todonotes} % to disable annotations on margins

@@

We have recorded the computation times for the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model with homogeneous and variable density at different heights (see Figure \ref{fig:speed-comparison}).
Firstly, we can see that both codes take more time to compute the gravity field for lower heights due to the increased divisions of the tesseroid in such cases.
Secondly, we can see that the homogeneous density code is up to twice faster than the new variable density algorithm for lower heights. However, the computation times gets more similar values at greater heights. In conclusion, the new variable density code is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/speed-comparison.pdf}
\caption{Computation times for a single tesseroid model with homogeneous and variable density at different heights.}
\label{fig:speed-comparison}
\end{figure}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
%~ \usepackage{todonotes} % to make annotations on margins
\usepackage[disable]{todonotes} % to disable annotations on margins

@@

We have recorded the computation times for the gravity potential, the gradient component $g_z$ and the Marussi tensor component $g_{zz}$ generated by a single tesseroid model with homogeneous ($\Delta t_\text{homogeneous}$) and variable ($\Delta 
t_\text{variable}$) density at different heights. Then we plotted the ratio between these computation times (see Figure \ref{fig:speed-comparison}):

\begin{equation}
    \text{Computation Times Ratio} =
        \frac{\Delta t_\text{variable}}{\Delta t_\text{homogeneous}}
    \label{eq:computation-times-ratio}
\end{equation}

From these results We can conclude that the homogeneous density code is up to twice faster than the new variable density algorithm for lower heights. However, the computation times ratio gets lower at greater heights, due to the reduction of the divisions made by the adaptive discretization algorithm. In summary, the new variable density code is fast enough to perform the calculations of a real model in a few minutes. \todo{real, esta bien la expresion?}

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/speed-comparison.pdf}
\caption{Computation times ratio between a single tesseroid model with variable and with homogeneous density at different heights, defined in equation \ref{eq:computation-times-ratio}.}
\label{fig:speed-comparison}
\end{figure}
